The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-10 paper/ms.tex
more citations for boyajian's star

Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect. Another star with a hump-and-spike spectrum is Boyajian's~Star, which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}. It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.
\citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. The other example is the B3e star HD~183362 at $G = -2.576$. A detailed study of these stars will be presented by Antoci et al., in prep.

@@

\section{Conclusions}
\label{conclusions}
\newpage

>>>>

Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect. Another star with a hump-and-spike spectrum is Boyajian's~Star, which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}. The dimming, which is chromatic in the manner expected of heterogeneous clouds of circumstellar dust in the line of sight \citep{2018ApJ...853..130D,2018arXiv180608842B}, has been ascribed to various causes \citep[reviewed in][]{2018RNAAS...2a..16W}, most notably a cloud of exocomets surrounding the star \citep[e.g.][]{2018MNRAS.473.5286W}. It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.
\citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. The other example is the B3e star HD~183362 at $G = -2.576$. A detailed study of these stars will be presented by Antoci et al., in prep.

@@

\section{Conclusions}
\label{conclusions}
